HerMES: ALMA Imaging of {\it Herschel}$^{\dagger}$-selected Dusty Star-forming Galaxies

### 2015-04-20 LaTeX/ms.tex
Fialkov comments.

%./authors_list hermes_authors_data_dr1_20121108.txt apj rsb dr fialkov scudders hayward cowley almalens
\author{R.~S.~Bussmann\altaffilmark{1},
D.~Riechers\altaffilmark{1},
A.~Fialkov\altaffilmark{2},
J.~M.~Scudder\altaffilmark{3},
C.~C.~Hayward\altaffilmark{4,5},
W.~Cowley\altaffilmark{6},
J.~Bock\altaffilmark{7,8},
J.~Calanog\altaffilmark{9},
S.~C.~Chapman\altaffilmark{10},
A.~Cooray\altaffilmark{9},
F.~De Bernardis\altaffilmark{9},
D.~Farrah\altaffilmark{11},
Hai~Fu\altaffilmark{12},
R.~Gavazzi\altaffilmark{13},
R.~Hopwood\altaffilmark{14},
R.~J.~Ivison\altaffilmark{15,16},
M.~Jarvis\altaffilmark{17},
C.~Lacey\altaffilmark{6},
A.~Loeb\altaffilmark{5},
S.~J.~Oliver\altaffilmark{3},
I.~P{\'e}rez-Fournon\altaffilmark{18,19},
D.~Rigopoulou\altaffilmark{20,21},
I.~G.~Roseboom\altaffilmark{3,16},
Douglas~Scott\altaffilmark{22},
A.~J.~Smith\altaffilmark{3},
J.~D.~Vieira\altaffilmark{23},
L.~Wang\altaffilmark{3},
J.~Wardlow\altaffilmark{24}}
\altaffiltext{$\dagger$}{Herschel is an ESA space observatory with science
instruments provided by European-led Principal Investigator consortia and with
important participation from NASA.}
\altaffiltext{1}{Department of Astronomy, Space Science Building, Cornell University, Ithaca, NY, 14853-6801}
\altaffiltext{2}{Departement de Physique, Ecole Normale Sup erieure, CNRS, 24 rue Lhomond, Paris, 75005 France}
\altaffiltext{3}{Astronomy Centre, Dept. of Physics \& Astronomy, University of Sussex, Brighton BN1 9QH, UK}
\altaffiltext{4}{TAPIR 350-17, California Institute of Technology, 1200 E. California Boulevard, Pasadena, CA 91125}
\altaffiltext{5}{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
\altaffiltext{6}{Institute for Computational Cosmology, Department of Physics, University of Durham, South Road, Durham, DH1 3LE, UK}
\altaffiltext{7}{California Institute of Technology, 1200 E. California Blvd., Pasadena, CA 91125}
\altaffiltext{8}{Jet Propulsion Laboratory, 4800 Oak Grove Drive, Pasadena, CA 91109}
\altaffiltext{9}{Dept. of Physics \& Astronomy, University of California, Irvine, CA 92697}
\altaffiltext{10}{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK}
\altaffiltext{11}{Department of Physics, Virginia Tech, Blacksburg, VA 24061}
\altaffiltext{12}{Department of Physics and Astronomy, The University of Iowa, 203 Van Allen Hall, Iowa City, IA 52242}
\altaffiltext{13}{Institut d'Astrophysique de Paris, UMR 7095, CNRS, UPMC Univ. Paris 06, 98bis boulevard Arago, F-75014 Paris, France}
\altaffiltext{14}{Astrophysics Group, Imperial College London, Blackett Laboratory, Prince Consort Road, London SW7 2AZ, UK}
\altaffiltext{15}{UK Astronomy Technology Centre, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK}
\altaffiltext{16}{Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK}
\altaffiltext{17}{Centre for Astrophysics Research, University of Hertfordshire, College Lane, Hatfield, Hertfordshire AL10 9AB, UK}
\altaffiltext{18}{Instituto de Astrof{\'\i}sica de Canarias (IAC), E-38200 La Laguna, Tenerife, Spain}
\altaffiltext{19}{Departamento de Astrof{\'\i}sica, Universidad de La Laguna (ULL), E-38205 La Laguna, Tenerife, Spain}
\altaffiltext{20}{RAL Space, Rutherford Appleton Laboratory, Chilton, Didcot, Oxfordshire OX11 0QX, UK}
\altaffiltext{21}{Department of Astrophysics, Denys Wilkinson Building, University of Oxford, Keble Road, Oxford OX1 3RH, UK}
\altaffiltext{22}{Department of Physics \& Astronomy, University of British Columbia, 6224 Agricultural Road, Vancouver, BC V6T~1Z1, Canada}
\altaffiltext{23}{Department of Astronomy and Department of Physics, University of Illinois, 1002 West Green Street, Urbana, IL 61801}
\altaffiltext{24}{Dark Cosmology Centre, Niels Bohr Institute, University of Copenhagen, Juliane Maries Vej 30, 2100 Copenhagen, Denmark}

@@

In detail, two of the sources in the {\it Herschel}-ALMA sample (HXMM01 and
HXMM02) overlap with the ``confirmed lensed'' sample in \citet{Wardlow:2013lr}
as well as with the {\it Herschel}-SMA sample in \citet{Bussmann:2013lr}.  A
further eght appear in the ``Supplementary sample'' of \citet{Wardlow:2013lr}.
The remainder have $S_{500} < 80\,$mJy and thus do not appear in
\citet{Wardlow:2013lr}.

@@

To describe $\rho_{\rm lens}\,(r)$, we use a superposition of a singular
isothermal sphere (SIS) and a Navarro-Frenk-White (NFW) profile
\citep{Navarro:1997ys} that is truncated at the virial radius.  The NFW profile
describes the outskirts of dark matter halos better, while the SIS profile is
preferred on smaller scales because it correctly fits the observed flat
rotational curves in galaxies.  We make sure that the resulting probability
density of lensing, $P\,(\mu)$, is normalized to unity.  To describe $n_{\rm
lens}\,(M, \, z)$, we generate the abundance of halos at each mass and redshift
using the \citet{Sheth:1999kx} formalism.  To describe $dN_{\rm source}/dz$, we
adopt the following redshift distribution which is based on photometric
redshifts of optical counterparts to ALMA sources identified in ALESS
\citep{Simpson:2014lr}:

@@

We explore two intrinsic luminosity functions that are intended to bracket the
plausible range of values for DSFGs based on two interferometric surveys.  One
is the luminosity function measured in ALESS \citep{Karim:2013lr}, and the
other is from interferometric follow-up of the first AzTEC survey in COSMOS
\citep{Scott:2008qy} using the SMA \citep{Younger:2007fk, Younger:2009lr} and
PdBI \citep{Miettinen:2015lr}.  These interferometric observations have shown
show that all of the sources in their surveys are either unlensed or lensed by
magnification factors $<2$.  This is why the ALESS and COSMOS luminosity
functions represent a plausible range of intrinsic luminosity functions for
DSFGs.  These luminosity functions are shown in the left panel of
Figure~\ref{fig:lensstats}.  Interferometric follow-up data in COSMOS
\citep{Smolcic:2012zl} and GOODS-N \citep{Barger:2012yg} are published, but
unknown completeness corrections in the single-dish surveys on which these
follow-up datasets are based precludes their use here.

@@

Both models tested in this paper exhibit a sharp transition from low
probability to high probability of being lensed, consistent with the data.
However, there are significant differences in where this transition flux
density, $S_{\rm trans}$, occurs --- i.e., where $P(\mu>\mu_{870}$ > 2).  In
the data, the logistic regression fit yields $S_{\rm trans} = 24\pm3\,$mJy
(error accounts only for statistical uncertainty in $S_{870}$ and $\mu_{870}$),
whereas the models based on the ALESS and COSMOS luminosity functions yield
$S_{\rm trans} = 37\,$mJy $S_{\rm trans} = 69\,$mJy, respectively.

Note caveats.

>>>>

%./authors_list hermes_authors_data_dr1_20121108.txt apj rsb dr fialkov scudders hayward cowley almalens
\author{R.~S.~Bussmann\altaffilmark{1},
D.~Riechers\altaffilmark{1},
A.~Fialkov\altaffilmark{2},
J.~Scudders\altaffilmark{3},
C.~C.~Hayward\altaffilmark{4,5},
W.~Cowley\altaffilmark{6},
J.~Bock\altaffilmark{7,8},
J.~Calanog\altaffilmark{9},
S.~C.~Chapman\altaffilmark{10},
A.~Cooray\altaffilmark{9},
F.~De Bernardis\altaffilmark{9},
D.~Farrah\altaffilmark{11},
Hai~Fu\altaffilmark{12},
R.~Gavazzi\altaffilmark{13},
R.~Hopwood\altaffilmark{14},
R.~J.~Ivison\altaffilmark{15,16},
M.~Jarvis\altaffilmark{17},
C.~Lacey\altaffilmark{6},
A.~Loeb\altaffilmark{5},
S.~J.~Oliver\altaffilmark{3},
I.~P{\'e}rez-Fournon\altaffilmark{18,19},
D.~Rigopoulou\altaffilmark{20,21},
I.~G.~Roseboom\altaffilmark{3,16},
Douglas~Scott\altaffilmark{22},
A.~J.~Smith\altaffilmark{3},
J.~D.~Vieira\altaffilmark{23},
L.~Wang\altaffilmark{3},
J.~Wardlow\altaffilmark{24}}
\altaffiltext{$\dagger$}{Herschel is an ESA space observatory with science
instruments provided by European-led Principal Investigator consortia and with
important participation from NASA.}
\altaffiltext{1}{Department of Astronomy, Space Science Building, Cornell University, Ithaca, NY, 14853-6801}
\altaffiltext{2}{Departement de Physique, Ecole Normale Superieure, CNRS, 24 rue Lhomond, 75005 Paris, France}
\altaffiltext{3}{Astronomy Centre, Dept. of Physics \& Astronomy, University of Sussex, Brighton BN1 9QH, UK}
\altaffiltext{4}{TAPIR 350-17, California Institute of Technology, 1200 E. California Boulevard, Pasadena, CA 91125}
\altaffiltext{5}{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
\altaffiltext{6}{Institute for Computational Cosmology, Department of Physics, University of Durham, South Road, Durham, DH1 3LE, UK}
\altaffiltext{7}{California Institute of Technology, 1200 E. California Blvd., Pasadena, CA 91125}
\altaffiltext{8}{Jet Propulsion Laboratory, 4800 Oak Grove Drive, Pasadena, CA 91109}
\altaffiltext{9}{Dept. of Physics \& Astronomy, University of California, Irvine, CA 92697}
\altaffiltext{10}{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK}
\altaffiltext{11}{Department of Physics, Virginia Tech, Blacksburg, VA 24061}
\altaffiltext{12}{Department of Physics and Astronomy, The University of Iowa, 203 Van Allen Hall, Iowa City, IA 52242}
\altaffiltext{13}{Institut d'Astrophysique de Paris, UMR 7095, CNRS, UPMC Univ. Paris 06, 98bis boulevard Arago, F-75014 Paris, France}
\altaffiltext{14}{Astrophysics Group, Imperial College London, Blackett Laboratory, Prince Consort Road, London SW7 2AZ, UK}
\altaffiltext{15}{UK Astronomy Technology Centre, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK}
\altaffiltext{16}{Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK}
\altaffiltext{17}{Centre for Astrophysics Research, University of Hertfordshire, College Lane, Hatfield, Hertfordshire AL10 9AB, UK}
\altaffiltext{18}{Instituto de Astrof{\'\i}sica de Canarias (IAC), E-38200 La Laguna, Tenerife, Spain}
\altaffiltext{19}{Departamento de Astrof{\'\i}sica, Universidad de La Laguna (ULL), E-38205 La Laguna, Tenerife, Spain}
\altaffiltext{20}{RAL Space, Rutherford Appleton Laboratory, Chilton, Didcot, Oxfordshire OX11 0QX, UK}
\altaffiltext{21}{Department of Astrophysics, Denys Wilkinson Building, University of Oxford, Keble Road, Oxford OX1 3RH, UK}
\altaffiltext{22}{Department of Physics \& Astronomy, University of British Columbia, 6224 Agricultural Road, Vancouver, BC V6T~1Z1, Canada}
\altaffiltext{23}{Department of Astronomy and Department of Physics, University of Illinois, 1002 West Green Street, Urbana, IL 61801}
\altaffiltext{24}{Dark Cosmology Centre, Niels Bohr Institute, University of
Copenhagen, Juliane Maries Vej 30, 2100 Copenhagen, Denmark}

@@

In detail, two of the sources in the {\it Herschel}-ALMA sample (HXMM01 and
HXMM02) overlap with the ``confirmed lensed'' sample in \citet{Wardlow:2013lr}
as well as with the {\it Herschel}-SMA sample in \citet{Bussmann:2013lr}.  A
further eight appear in the ``Supplementary sample'' of \citet{Wardlow:2013lr}.
The remainder have $S_{500} < 80\,$mJy and thus do not appear in
\citet{Wardlow:2013lr}.

@@

To describe $\rho_{\rm lens}\,(r)$, we use a superposition of a singular
isothermal sphere (SIS) and a Navarro-Frenk-White (NFW) profile
\citep{Navarro:1997ys} that is truncated at the virial radius.  The NFW profile
describes the outskirts of dark matter halos better \citep{Mandelbaum:2005lr},
while the SIS profile is preferred on smaller scales because it correctly fits
the observed flat rotational curves in galaxies \citep{Kochanek:1994fk}.  We
make sure that the resulting probability density of lensing, $P\,(\mu)$, is
normalized to unity.  To describe $n_{\rm lens}\,(M, \, z)$, we generate the
abundance of halos at each mass and redshift using the \citet{Sheth:1999kx}
formalism.  To describe $dN_{\rm source}/dz$, we adopt the following redshift
distribution which is based on photometric redshifts of optical counterparts to
ALMA sources identified in ALESS \citep{Simpson:2014lr}:

@@

We explore two intrinsic luminosity functions that are intended to bracket the
plausible range of values for DSFGs based on two interferometric surveys.  One
is the luminosity function measured in ALESS \citep{Karim:2013lr}, and the
other is from interferometric follow-up of the first AzTEC survey in COSMOS
\citep{Scott:2008qy} using the SMA \citep{Younger:2007fk, Younger:2009lr} and
PdBI \citep{Miettinen:2015lr}.  These interferometric observations have shown
that all of the sources in their surveys are either unlensed or lensed by
magnification factors $<2$.  This is why the ALESS and COSMOS luminosity
functions represent a plausible range of intrinsic luminosity functions for
DSFGs.  These luminosity functions are shown in the left panel of
Figure~\ref{fig:lensstats}.  Interferometric follow-up data in COSMOS
\citep{Smolcic:2012zl} and GOODS-N \citep{Barger:2012yg} are published, but
unknown completeness corrections in the single-dish surveys on which these
follow-up datasets are based precludes their use here.

@@

Both models tested in this paper exhibit a sharp transition from low
probability to high probability of being lensed, consistent with the data.
However, there are significant differences in where this transition flux
density, $S_{\rm trans}$, occurs --- i.e., where $P(\mu>\mu_{870}) > 2$.  In
the data, the logistic regression fit yields $S_{\rm trans} = 24\pm3\,$mJy
(error accounts only for statistical uncertainty in $S_{870}$ and $\mu_{870}$),
whereas the models based on the ALESS and COSMOS luminosity functions yield
$S_{\rm trans} = 37\,$mJy $S_{\rm trans} = 69\,$mJy, respectively.
